
\section{Computation of Order Bases}

\label{sec:Order-Basis-Computation}

In this section, we establish a link between two different Storjohann
transformed problems by dividing the transformed problem from the
previous section to two subproblems and then simplifying the second
subproblem. This leads to a recursive way of computing order bases.
We then describe our algorithm in the equivalent iterative way.


\subsection{\label{sub:Dividing-to-Subproblems}Dividing to Subproblems }

\prettyref{sec:transform} shows that the problem of computing a $\left(\mathbf{F},\sigma,\vec{s}\right)$-basis
can be converted to the problem of computing a $(\check{\mathbf{F}},\vec{\omega},\vec{s'})$-basis
and more generally, computing a $(\bar{\mathbf{F}}^{\left(i\right)},2\delta^{\left(i\right)},\vec{s}^{\left(i\right)})$-basis,
a Storjohann transformed problem with degree parameter $\delta^{\left(i\right)}$,
can be converted to a $(\check{\mathbf{F}}^{\left(i\right)},\vec{\omega}^{\left(i\right)},\vec{s}^{\left(i-1\right)})$-basis
computation problem. We now consider dividing the new converted problem
to two subproblems.

The first subproblem is to compute a $(\check{\mathbf{F}}^{\left(i\right)},2\delta^{\left(i-1\right)},\vec{s}^{\left(i-1\right)})$-basis
or equivalently a $(\bar{\mathbf{F}}^{\left(i-1\right)},2\delta^{\left(i-1\right)},\vec{s}^{\left(i-1\right)})$-basis
$\bar{\mathbf{P}}^{\left(i-1\right)}$. This is another Storjohann
transformed problem with degree parameter $\delta^{\left(i-1\right)}$.
The second subproblem is computing a $(\check{\mathbf{F}}^{\left(i\right)}\bar{\mathbf{P}}^{\left(i-1\right)},\vec{\omega}^{\left(i\right)},\vec{t}^{\left(i-1\right)})$-basis
$\bar{\mathbf{Q}}^{\left(i\right)}$ using the residual $\check{\mathbf{F}}^{\left(i\right)}\bar{\mathbf{P}}^{\left(i-1\right)}$
from the first subproblem along with a degree shift $\vec{t}^{\left(i-1\right)}=\deg_{\vec{s}^{\left(i-1\right)}}\bar{\mathbf{P}}^{\left(i-1\right)}$.
From Theorem 5.1 in \citep{BL1997} we then know that the product
$\bar{\mathbf{P}}^{\left(i-1\right)}\bar{\mathbf{Q}}^{\left(i\right)}$
is a $(\check{\mathbf{F}}^{\left(i\right)},\vec{\omega}^{\left(i\right)},\vec{s}^{\left(i-1\right)})$-basis
and $\deg_{\vec{s}^{\left(i-1\right)}}\bar{\mathbf{P}}^{\left(i-1\right)}\bar{\mathbf{Q}}^{\left(i\right)}=\deg_{\vec{t}^{\left(i-1\right)}}\bar{\mathbf{Q}}^{\left(i\right)}$. 
\begin{exmp}
\label{exm:subproblems} Let us continue with \prettyref{exm:StorjohannTransformation}
and \prettyref{exm:auxiliaryTransformation} to compute a $\left(\mathbf{F},8,\vec{0}\right)$-basis
( or equivalently a $(\bar{\mathbf{F}}^{\left(2\right)},8,\vec{0})$-basis).
This can be determined by computing a $(\check{\mathbf{F}}^{\left(2\right)},[8,4,4],\vec{0})$-basis
as shown in \prettyref{exm:auxiliaryTransformation} with $\check{\mathbf{F}}^{\left(2\right)}=\check{\mathbf{F}}$
from \prettyref{exm:auxiliaryTransformation}. Computing a $(\check{\mathbf{F}}^{\left(2\right)},[8,4,4],\vec{0})$-basis
can be divided to two subproblems. The first subproblem is computing
a $(\bar{\mathbf{F}}^{\left(1\right)},4,\vec{0})$-basis $\bar{\mathbf{P}}^{\left(1\right)}$,
the Storjohann partial linearized problem in \prettyref{exm:StorjohannTransformation}.
The residual \[
\check{\mathbf{F}}^{(2)}\bar{\mathbf{P}}^{(1)}=\left[{\begin{array}{rcccccccccc}
0 & \  & x^{8} & \  & x^{6}+x^{9} & \  & x^{4}+x^{6}+x^{9} & \  & x^{6}+x^{8}+x^{9}+x^{10} & \  & x^{5}+x^{8}\\
0 &  & 0 &  & x^{5} &  & x^{4}+x^{6} &  & x^{4}+x^{6} &  & x^{5}+x^{6}\\
0 &  & x^{4} &  & x^{5} &  & x^{5} &  & x^{4}+x^{5}+x^{6} &  & x^{4}\end{array}}\right]\]
 is then used as the input matrix for the second subproblem. The shift
for the second subprobem $\vec{t}^{(1)}=[0,1,2,3,3,3]$ is the list
of column degrees of $\bar{\mathbf{P}}^{(1)}$ and so the second subproblem
is to compute a $(\check{\mathbf{F}}^{(2)}\bar{\mathbf{P}}^{(1)},\left[8,4,4\right],[0,1,2,3,3,3])$-basis,
which is \begin{equation}
\bar{\mathbf{Q}}^{(2)}=\left[{\begin{array}{cccccc}
~1~ & ~0~ & 0 & 0 & 0 & 0\\
0 & 1 & 0 & 0 & 0 & 0\\
0 & 0 & 1 & ~x^{2}~ & ~x~ & ~1~\\
0 & 0 & 0 & 0 & x & 0\\
0 & 0 & 1 & 0 & 0 & 0\\
0 & 0 & 0 & 0 & 1 & ~x~\end{array}}\right],\label{eq:Qbar2}\end{equation}
 $\bar{\mathbf{P}}^{(1)}\bar{\mathbf{Q}}^{(2)}$ then gives the $(\check{\mathbf{F}}^{\left(2\right)},[8,4,4],\vec{0})$-basis
shown in \prettyref{exm:auxiliaryTransformation}. 
\end{exmp}
We now show that the dimension of the second subproblem can be significantly
reduced. First, the row dimension can be reduced by over a half. Let
$\hat{\mathbf{P}}^{\left(i-1\right)}=\mathbf{E}^{\left(i\right)}\bar{\mathbf{P}}^{\left(i-1\right)}$. 
\begin{lem}
\label{lem:simplifySecondSubproblem}A $(\bar{\mathbf{F}}^{\left(i\right)}\hat{\mathbf{P}}^{\left(i-1\right)},2\delta^{\left(i\right)},\vec{t}^{\left(i-1\right)})$-basis
is a $(\check{\mathbf{F}}^{\left(i\right)}\bar{\mathbf{P}}^{\left(i-1\right)},\vec{\omega}^{\left(i\right)},\vec{t}^{\left(i-1\right)})$-basis.\end{lem}
\begin{pf}
This follows because $\bar{\mathbf{F}}^{\left(i\right)}\hat{\mathbf{P}}^{\left(i-1\right)}$
is a submatrix of $\check{\mathbf{F}}^{\left(i\right)}\bar{\mathbf{P}}^{\left(i-1\right)}$
after removing rows already having the correct order $2\delta^{\left(i-1\right)}$. 
\end{pf}
The column dimension of the second subproblem can be reduced by disregarding
the $(\bar{\mathbf{F}}^{\left(i\right)},2\delta^{\left(i\right)},\vec{s}^{\left(i\right)})_{\delta^{\left(i-1\right)}-1}$-basis
already computed. More specifically, after sorting the columns of
$\bar{\mathbf{P}}^{\left(i-1\right)}$ in an increasing order of their
$\vec{s}^{\left(i-1\right)}$-degrees, let $[\bar{\mathbf{P}}_{1}^{\left(i-1\right)},\bar{\mathbf{P}}_{2}^{\left(i-1\right)}]=\bar{\mathbf{P}}^{\left(i-1\right)}$
be such that $\deg_{\vec{s}^{\left(i-1\right)}}\bar{\mathbf{P}}_{1}^{\left(i-1\right)}\le\delta^{\left(i-1\right)}-1$
and $\deg_{\vec{s}^{\left(i-1\right)}}\bar{\mathbf{P}}_{2}^{\left(i-1\right)}\ge\delta^{\left(i-1\right)}$.
Then $\hat{\mathbf{P}}_{1}^{\left(i-1\right)}=\mathbf{E}^{\left(i\right)}\bar{\mathbf{P}}_{1}^{\left(i-1\right)}$
is a $(\bar{\mathbf{F}}^{\left(i\right)},2\delta^{\left(i\right)},\vec{s}^{\left(i\right)})_{\delta^{\left(i-1\right)}-1}$-basis
by \prettyref{lem:linkStorjohanTransform}. In the second subproblem,
the remaining basis elements of a $(\bar{\mathbf{F}}^{\left(i\right)},2\delta^{\left(i\right)},\vec{s}^{\left(i\right)})$-basis
can then be computed without $\bar{\mathbf{P}}_{1}^{\left(i-1\right)}$.

Let $\hat{\mathbf{P}}_{2}^{\left(i-1\right)}=\mathbf{E}^{\left(i\right)}\bar{\mathbf{P}}_{2}^{\left(i-1\right)}$,
$\vec{b}^{\left(i-1\right)}=\deg_{\vec{s}^{\left(i-1\right)}}\bar{\mathbf{P}}_{2}^{\left(i-1\right)}$,
$\bar{\mathbf{Q}}_{2}^{\left(i\right)}$ be a $(\bar{\mathbf{F}}^{\left(i\right)}\hat{\mathbf{P}}_{2}^{\left(i-1\right)},2\delta^{\left(i\right)},\vec{b}^{\left(i-1\right)})$-basis
(or equivalently a $(\check{\mathbf{F}}^{\left(i\right)}\bar{\mathbf{P}}_{2}^{\left(i-1\right)},\vec{\omega}^{\left(i\right)},\vec{b}^{\left(i-1\right)})$-basis),
and $k^{\left(i-1\right)}$ be the column dimension of $\bar{\mathbf{P}}_{1}^{\left(i-1\right)}$.
Then 
\begin{lem}
\label{lem:disregardComputedBasisElements} The matrix \[
\bar{\mathbf{Q}}^{\left(i\right)}=\left[\begin{array}{cc}
\mathbf{I}_{k^{\left(i-1\right)}}\\
 & \bar{\mathbf{Q}}_{2}^{\left(i\right)}\end{array}\right]\]
 is a $(\bar{\mathbf{F}}^{\left(i\right)}\hat{\mathbf{P}}^{\left(i-1\right)},2\delta^{\left(i\right)},\vec{t}^{\left(i-1\right)})$-basis
(equivalently a $(\check{\mathbf{F}}^{\left(i\right)}\bar{\mathbf{P}}^{\left(i-1\right)},\vec{\omega}^{\left(i\right)},\vec{t}^{\left(i-1\right)})$-basis).\end{lem}
\begin{pf}
First note that $\bar{\mathbf{Q}}^{\left(i\right)}$ has order $(\bar{\mathbf{F}}^{\left(i\right)}\hat{\mathbf{P}}^{\left(i-1\right)},2\delta^{\left(i\right)})$
as \[
\bar{\mathbf{F}}^{\left(i\right)}\hat{\mathbf{P}}^{\left(i-1\right)}\bar{\mathbf{Q}}^{\left(i\right)}=[\bar{\mathbf{F}}^{\left(i\right)}\hat{\mathbf{P}}_{1}^{\left(i-1\right)},\bar{\mathbf{F}}^{\left(i\right)}\hat{\mathbf{P}}_{2}^{\left(i-1\right)}\bar{\mathbf{Q}}_{2}^{\left(i\right)}]\equiv0\mod x^{2\delta^{\left(i\right)}}.\]
 In addition, $\bar{\mathbf{Q}}^{\left(i\right)}$ has minimal $\vec{t}^{\left(i-1\right)}$
degrees as $\bar{\mathbf{Q}}_{2}^{\left(i\right)}$ is $\vec{b}$-minimal.
Hence $\bar{\mathbf{Q}}^{\left(i\right)}$ is a $(\bar{\mathbf{F}}^{\left(i\right)}\cdot\hat{\mathbf{P}}^{\left(i-1\right)},2\delta^{\left(i\right)},\vec{t}^{\left(i-1\right)})$-basis
by \prettyref{lem:orderBasisEquivalence}. 
\end{pf}
%
\begin{comment}
Alternatively, one can also argue that since $\hat{\mathbf{P}}_{1}^{\left(i-1\right)}$
already has order $(\bar{\mathbf{F}}^{\left(i\right)},2\delta^{\left(i\right)})$,
it cannot contribute in any way to and cannot be affected in any way
by the computations of a $(\bar{\mathbf{F}}^{\left(i\right)}\hat{\mathbf{P}}^{\left(i-1\right)},2\delta^{\left(i\right)},\vec{b}^{\left(i-1\right)})$-basis,
hence it is sufficient to just use $\bar{\mathbf{F}}^{\left(i\right)}\hat{\mathbf{P}}_{2}^{\left(i-1\right)}$
to compute a $(\bar{\mathbf{F}}^{\left(i\right)}\cdot\hat{\mathbf{P}}_{2}^{\left(i-1\right)},2\delta^{\left(i\right)},\vec{b}^{\left(i-1\right)})$-basis. 
\end{comment}
{}

\prettyref{lem:disregardComputedBasisElements} immediately leads
to the following. 
\begin{lem}
\label{lem:computationAtTopLevel}Let $\hat{\mathbf{S}}=[\hat{\mathbf{P}}_{1}^{\left(i-1\right)},\hat{\mathbf{P}}_{2}^{\left(i-1\right)}\bar{\mathbf{Q}}_{2}^{\left(i\right)}]$,
$I$ the column rank profile of $\lcoeff(x^{\vec{s}^{\left(i\right)}}\hat{\mathbf{S}})$.
Then $\hat{\mathbf{S}}_{I}$ is a $(\bar{\mathbf{F}}^{\left(i\right)},2\delta^{\left(i\right)},\vec{s}^{\left(i\right)})$-basis.\end{lem}
\begin{pf}
From \prettyref{lem:disregardComputedBasisElements}, $\bar{\mathbf{Q}}^{\left(i\right)}$
is a $(\check{\mathbf{F}}^{\left(i\right)}\bar{\mathbf{P}}^{\left(i-1\right)},\vec{\omega}^{\left(i\right)},\vec{t}^{\left(i-1\right)})$-basis
and hence $\bar{\mathbf{P}}^{\left(i-1\right)}\bar{\mathbf{Q}}^{\left(i\right)}$
is a $(\check{\mathbf{F}}^{\left(i\right)},\vec{\omega}^{\left(i\right)},\vec{s}^{\left(i-1\right)})$-basis.
Therefore \prettyref{thm:extractingOrderBasis} applies since $[\hat{\mathbf{P}}_{1}^{\left(i-1\right)},\hat{\mathbf{P}}_{2}^{\left(i-1\right)}\bar{\mathbf{Q}}_{2}^{\left(i\right)}]=\mathbf{E}^{\left(i\right)}\bar{\mathbf{P}}^{\left(i-1\right)}\bar{\mathbf{Q}}^{\left(i\right)}$.
%
\begin{comment}
$=\mathbf{E}^{\left(i\right)}[\bar{\mathbf{P}}_{1}^{\left(i-1\right)},\bar{\mathbf{P}}_{2}^{\left(i-1\right)}\bar{\mathbf{Q}}_{2}^{\left(i\right)}]$ 
\end{comment}
{}\end{pf}
\begin{exmp}
Continuing with \prettyref{exm:StorjohannTransformation}, \prettyref{exm:auxiliaryTransformation},
and \prettyref{exm:subproblems}, %
\begin{comment}
notice that after the first subproblem, the second subproblem of computing
$\bar{\mathbf{Q}}^{(2)}$ in \prettyref{exm:subproblems} is really
a smaller problem of computing the lower right $4\times4$ submatrix
$\bar{\mathbf{Q}}_{2}^{(2)}$, which is a $(\bar{\mathbf{F}}^{\left(2\right)}\hat{\mathbf{P}}_{2}^{\left(1\right)},8,\vec{b}^{\left(1\right)})$-basis
(or equivalently a $(\check{\mathbf{F}}^{\left(2\right)}\bar{\mathbf{P}}_{2}^{\left(1\right)},[8,4,4],\vec{b}^{\left(1\right)})$-basis),
where $\bar{\mathbf{P}}_{2}^{\left(1\right)}$ is the last $4$ columns
of $\bar{\mathbf{P}}^{(1)}$, $\vec{b}^{(1)}=[2,3,3,3]$ is the list
of column degrees of $\bar{\mathbf{P}}_{2}^{(1)}$, and $\hat{\mathbf{P}}_{2}^{\left(1\right)}$
is the first $4$ rows of $\bar{\mathbf{P}}_{2}^{(1)}$. 
\end{comment}
{}notice that in the computation of the second subproblem, instead of
using $\check{\mathbf{F}}^{\left(2\right)},$ $\bar{\mathbf{P}}^{\left(1\right)}$,
$\bar{\mathbf{Q}}^{(2)}$, and $\bar{\mathbf{P}}^{(1)}\bar{\mathbf{Q}}^{(2)}$,
the previous lemmas show that we can just use their submatrices, $\bar{\mathbf{F}}^{(2)}$
the top left $1\times4$ submatrix of $\check{\mathbf{F}}^{\left(2\right)}$,
$\hat{\mathbf{P}}_{2}^{(1)}$ the top right $4\times4$ submatrix
of $\bar{\mathbf{P}}^{(1)}$, $\bar{\mathbf{Q}}_{2}^{(2)}$ the bottom
right $4\times4$ submatrix of $\bar{\mathbf{Q}}^{(2)}$, and $\hat{\mathbf{P}}_{2}^{(1)}\bar{\mathbf{Q}}_{2}^{(2)}$
the top right $4\times4$ submatrix of $\bar{\mathbf{P}}^{(1)}\bar{\mathbf{Q}}^{(2)}$of
lower dimensions. 
\end{exmp}
\prettyref{lem:computationAtTopLevel} gives us a way of computing
a $\left(\mathbf{F},\sigma,\vec{s}\right)$-basis. We can set $i$
to $\log\left(n/m\right)-1$ so that $(\bar{\mathbf{F}}^{\left(i\right)},2\delta^{\left(i\right)},\vec{s}^{\left(i\right)})$=$\left(\mathbf{F},\sigma,\vec{s}\right)$,
and compute a $(\bar{\mathbf{F}}^{\left(i\right)},2\delta^{\left(i\right)},\vec{s}^{\left(i\right)})$-basis.
By \prettyref{lem:computationAtTopLevel}, this can be divided into
two subproblems. The first produces $[\hat{\mathbf{P}}_{1}^{\left(i-1\right)},\hat{\mathbf{P}}_{2}^{\left(i-1\right)}]=\hat{\mathbf{P}}^{\left(i-1\right)}=\mathbf{E}^{\left(i\right)}\bar{\mathbf{P}}^{\left(i-1\right)}$
from computing a $(\bar{\mathbf{F}}^{\left(i-1\right)},\delta^{\left(i-1\right)},\vec{s}^{\left(i-1\right)})$-basis
$\bar{\mathbf{P}}^{\left(i-1\right)}$. The second subproblem then
computes a $(\bar{\mathbf{F}}^{\left(i\right)}\hat{\mathbf{P}}_{2}^{\left(i-1\right)},2\delta^{\left(i\right)},\vec{b}^{\left(i-1\right)})$-basis
$\bar{\mathbf{Q}}_{2}^{\left(i\right)}$. Note the first subproblem
of computing a $(\bar{\mathbf{F}}^{\left(i-1\right)},\delta^{\left(i-1\right)},\vec{s}^{\left(i-1\right)})$-basis
can again be divided to two subproblems just as before. This can be
repeated recursively until we reach the base case with degree parameter
$\delta^{\left(1\right)}=2d$. The total levels of recursion is therefore
$\log\left(n/m\right)-1$.

Notice that the transformed matrix $\check{\mathbf{F}}^{\left(i\right)}$
is not used explicitly in the computation, even though it is crucial
for deriving our results.


\subsection{The Iterative View}

In this subsection we present our algorithm, which uses an iterative
version of the computation discussed above.%
\begin{comment}
The recursive top-down approach of the previous subsection is useful
for giving an overall picture of the computation process. Algorithm
\prettyref{alg:mab} uses an equivalent corresponding bottom-up iterative
approach. 
\end{comment}
{}%
\begin{comment}
, allowing the complexity to be more easily analyzed. 
\end{comment}
{}%
\begin{comment}
. In practice, bottom-up iterative approaches are more efficient than
the corresponding top-down recursive approaches. For our purpose,
it is also easier to analyze the computational cost of the iterative
procedure. 
\end{comment}
{}

\prettyref{alg:mab} uses a subroutine $\mab$, the algorithm from
Giorgi et al. \citeyearpar{Giorgi2003}, for computing order bases
with balanced input. Specifically, $\left[\mathbf{Q},\vec{a}\right]=\mab(\mathbf{G},\sigma,\vec{b})$
computes a $(\mathbf{G},\sigma,\vec{b})$-basis and also returns its
$\vec{b}$-column degrees $\vec{a}$. The other subroutine $\StorjohannTransform$
is the transformation described in \prettyref{sub:storjohannTransformation}.

\prettyref{alg:mab} proceeds as follows. In the first iteration,
which is the base case of the recursive approach, we set the degree
parameter $\delta^{\left(1\right)}$ to be twice of the average degree
$d$ and apply Storjohann's transformation to produce a new input
matrix $\bar{\mathbf{F}}^{\left(1\right)}$, which has $l^{\left(1\right)}$
block rows. Then a $(\bar{\mathbf{F}}^{\left(1\right)},2\delta^{\left(1\right)},\vec{s}^{\left(1\right)})$-basis
$\bar{\mathbf{P}}^{\left(1\right)}$ is computed. Note this is in
fact the first subproblem of computing a $(\bar{\mathbf{F}}^{\left(2\right)},2\delta^{\left(2\right)},\vec{s}^{\left(2\right)})$-basis,
which is another Storjohann transformed problem and also the problem
of the second iteration. Now at the second iteration, we work on a
new Storjohann transformed problem with the degree doubled and the
number of block rows $l^{\left(2\right)}=(l^{\left(1\right)}-1)/2$
reduced by over a half. The column dimension is reduced by using the
result from the previous iteration. More specifically, we know that
a $\bar{\mathbf{P}}^{\left(1\right)}$ already provides a $(\bar{\mathbf{F}}^{\left(2\right)},2\delta^{\left(2\right)},\vec{s}^{\left(2\right)})_{\delta^{\left(1\right)}-1}$-basis
$\hat{\mathbf{P}}_{1}^{\left(1\right)}$, which can be disregarded
in the remaining computation. Now the remaining work in the second
iteration is to compute a $(\bar{\mathbf{F}}^{\left(2\right)}\hat{\mathbf{P}}_{2}^{\left(1\right)},2\delta^{\left(2\right)},\vec{b}^{\left(1\right)})$-basis
$\bar{\mathbf{Q}}^{\left(2\right)}$, where $\vec{b}^{\left(1\right)}=\deg_{\vec{s}^{\left(1\right)}}\bar{\mathbf{P}}_{2}^{\left(1\right)}$,
and then to combine it with the result from the previous iteration
to form a matrix $[\hat{\mathbf{P}}_{1}^{\left(1\right)},\hat{\mathbf{P}}_{2}^{\left(1\right)}\bar{\mathbf{Q}}^{\left(2\right)}]$
in order to extract a $(\bar{\mathbf{F}}^{\left(2\right)},2\delta^{\left(2\right)},\vec{s}^{\left(2\right)})$-basis
$\bar{\mathbf{P}}^{\left(2\right)}$.

With a $(\bar{\mathbf{F}}^{\left(2\right)},2\delta^{\left(2\right)},\vec{s}^{\left(2\right)})$-basis
computed, we can repeat the same process to use it for computing a
$(\bar{\mathbf{F}}^{\left(3\right)},2\delta^{\left(3\right)},\vec{s}^{\left(3\right)})$-basis.
Continue, using the computed $(\bar{\mathbf{F}}^{\left(i-1\right)},2\delta^{\left(i-1\right)},\vec{s}^{\left(i-1\right)})$-basis
to compute a $(\bar{\mathbf{F}}^{\left(i\right)},2\delta^{\left(i\right)},\vec{s}^{\left(i\right)})$-basis,
until all $n$ elements of a $\left(\mathbf{F},\sigma,\vec{s}\right)$-basis
have been determined.

\input{algorithm1.tex}

%
\begin{comment}
\begin{thm}
Algorithm \prettyref{alg:mab} computes a $\left(\mathbf{F},\sigma,\vec{s}\right)$-basis
correctly.\end{thm}
\begin{pf}
This follows from \prettyref{lem:simplifySecondSubproblem}, \prettyref{lem:disregardComputedBasisElements},
and \prettyref{lem:computationAtTopLevel}. 
\end{pf}

\end{comment}
{} 
